### 2020-06-08 submission/manuscript.tex
Updated version after modifying figure ledends

\includegraphics{figure_1.pdf} \textbf{Figure 1. Clindamycin is
sufficient to promote \emph{C. difficile} colonization regardless of
colony source, but clearance time varies across sources of C57BL/6
mice.} A. Setup of the experimental timeline. Mice for the experiments
were obtained from 6 different sources: the Schloss (N =8) and Young lab
(N = 9) colonies at the University of Michigan, the Jackson Laboratory
(N = 8), Charles River Laboratory (N = 8), Taconic Biosciences (N = 8),
and Envigo (N = 8). All mice were administered 10 mg/kg clindamycin
intraperitoneally (IP) 1 day before challenge with \emph{C. difficile}
630 spores on day 0. Mice were weighed and feces was collected daily
through the end of the experiment (9 days post-infection). Note: 3 mice
died during course of experiment. 1 Taconic mouse prior to infection and
1 Jackson and 1 Envigo mouse between 1- and 3-days post-infection. B.
\emph{C. difficile} CFU/gram stool measured over time (N = 20-49 mice
per timepoint) via serial dilutions. The black line represents the limit
of detection for the first serial dilution. CFU quantification data was
not available for each mouse due to early deaths, stool sampling
difficulties, and not plating all of the serial dilutions. C. Mouse
weight change measured in grams over time (N = 45-49 mice per
timepoint), all mice were normalized to the weight recorded 1 day before
infection. For B-C: timepoints where differences across sources of mice
were statistically significant by Kruskal-Wallis test with
Benjamini-Hochberg correction for testing across multiple days (Table S1
and Table S2) are reflected by the asterisk(s) above each timepoint (*,
P \textless{} 0.05, **, P \textless{} 0.01, ***, P \textless{} 0.001).
Lines represent the mean for each source and circles represent
individual mice. D. \emph{C. difficile} CFU status on Day 7 within each
mouse colony source. Mice were classified as colonized or cleared (not
detectable at the limit of detection of 100 CFU). Schloss (N = 6), Young
(N = 9), Jackson (N = 5), Charles River (N = 8), Taconic (N = 5), Envigo
(N = 7). Alternative: N = 5-9 mice per group.

@@

\includegraphics{figure_5.pdf} \textbf{Figure 5. Clindamycin treatment
has the same effects on a subset of taxa regardless of colony source.}
A-B. Boxplots of the top 10 most significant (adjusted P value
\textless{} 0.05) OTUs with relative abundances that changed post
clindamycin treatment. C-D. Boxplots of the top 10 most significant
families with relative abundances that changed post clindamycin
treatment. Data were analyzed by Wilcoxon signed rank test limited to
mice that had paired sequence data for day -1 and 0 (N = 31). Tests were
performed at the OTU and family level with Benjamini-Hochberg correction
for testing all identified OTUs and families. See Table S10-11 for
complete list of OTUs and families significantly impacted by clindamycin
treatment. The grey vertical line indicates the limit of detection for
A-D.

@@

\includegraphics{figure_S2.pdf} \textbf{Figure S2. Only bacterial
communities from University of Michigan mice significantly vary between
experiments.} A-F. PCoA of Theta YC distances for the baseline fecal
bacterial communities within each source of mice. Each symbol represents
a stool sample from an individual mouse with color corresponding to
experiment and shape representing cage mates. PERMANOVA was performed
within each group to examine the contributions of experiment and cage to
observed variation. Experiment number and cage only significantly
explained observed variation for mice from the Schloss (add r2 and P
values) and Young (add r2 and P values) lab colonies (Table S5).

@@

\includegraphics{figure_S3.pdf} \textbf{Figure S3. \emph{C. difficile}
colonization status 7 days post-infection varies across mice.} A. Bar
graph visualizations of overall day 7 classification outcomes used to
build logistic regression models. Mice were classified as colonized or
cleared (not detectable at the limit of detection of 100 CFU) based on
CFU g/stool data from 7 days post-infection. B-D. Classification input
data used for models based on day -1 (B), day 0 (C), and day 1 (D)
community relative abundance data. Only mice with day 7 \emph{C.
difficile} status and community relative abundance data for each
respective timepoint were used as input data for the classification
models.

@@

\textbf{Movie S1. Large shifts in bacterial community structure occurred
after clindamycin and \emph{C. difficile} infection.} PCoA of Theta YC
distances animated from 0 through 9 days post-infection. Transparency of
the circle corresponds to the day of the experiment, each circle
represents a sample from an individual mouse at a specific timepoint.
See Table S5 for PERMANOVA results).

>>>>

\includegraphics{figure_1.pdf} \textbf{Figure 1. Clindamycin is
sufficient to promote \emph{C. difficile} colonization regardless of
colony source, but clearance time varies across sources of C57BL/6
mice.} A. Setup of the experimental timeline. Mice for the experiments
were obtained from 6 different sources: the Schloss (N = 8) and Young
lab (N = 9) colonies at the University of Michigan, the Jackson
Laboratory (N = 8), Charles River Laboratory (N = 8), Taconic
Biosciences (N = 8), and Envigo (N = 8). All mice were administered 10
mg/kg clindamycin intraperitoneally (IP) 1 day before challenge with
\emph{C. difficile} 630 spores on day 0. Mice were weighed and feces was
collected daily through the end of the experiment (9 days
post-infection). Note: 3 mice died during course of experiment. 1
Taconic mouse prior to infection and 1 Jackson and 1 Envigo mouse
between 1- and 3-days post-infection. B. \emph{C. difficile} CFU/gram
stool measured over time (N = 20-49 mice per timepoint) via serial
dilutions. The black line represents the limit of detection for the
first serial dilution. CFU quantification data was not available for
each mouse due to early deaths, stool sampling difficulties, and not
plating all of the seriral dilutions. C. Mouse weight change measured in
grams over time (N = 45-49 mice per timepoint), all mice were normalized
to the weight recorded 1 day before infection. For B-C: timepoints where
differences across sources of mice were statistically significant by
Kruskal-Wallis test with Benjamini-Hochberg correction for testing
across multiple days (Table S1 and Table S2) are reflected by the
asterisk(s) above each timepoint (*, P \textless{} 0.05, **, P
\textless{} 0.01, ***, P \textless{} 0.001). Lines represent the mean
for each source and circles represent individual mice. D. \emph{C.
difficile} CFU status on Day 7 within each mouse colony source. Mice
were classified as colonized or cleared (not detectable at the limit of
detection of 100 CFU). N = 5-9 mice per group.

@@

\includegraphics{figure_5.pdf} \textbf{Figure 5. Clindamycin treatment
has the same effects on a subset of taxa regardless of colony source.}
A-B. Boxplots of the top 10 most significant (adjusted \emph{P} value
\textless{} 0.05) OTUs with relative abundances that changed post
clindamycin treatment. C-D. Boxplots of the top 10 most significant
families with relative abundances that changed post clindamycin
treatment. Data were analyzed by Wilcoxon signed rank test limited to
mice that had paired sequence data for day -1 and 0 (N = 31). Tests were
performed at the OTU and family levels with Benjamini-Hochberg
correction for testing all identified OTUs and families. See Table
S10-11 for complete list of OTUs and families significantly impacted by
clindamycin treatment. The grey vertical line indicates the limit of
detection for A-D.

@@

\includegraphics{figure_S2.pdf} \textbf{Figure S2. Only bacterial
communities from University of Michigan mice significantly vary between
experiments.} A-F. PCoA of Theta YC distances for the baseline fecal
bacterial communities within each source of mice. Each symbol represents
a stool sample from an individual mouse with color corresponding to
experiment and shape representing cage mates. PERMANOVA was performed
within each group to examine the contributions of experiment and cage to
observed variation. Experiment number and cage only significantly
explained observed variation for mice from the Schloss (combined
R\textsuperscript{2} = 0.99; \emph{P} \(\le\) 0.033) and Young (combined
R\textsuperscript{2} = 0.95; \emph{P} \(\le\) 0.029) lab colonies (Table
S7).

@@

\includegraphics{figure_S3.pdf} \textbf{Figure S3. \emph{C. difficile}
colonization status 7 days post-infection varies across mice.} A. Bar
graph visualizations of overall day 7 C. difficile colonization status
that were used as classification outcomes to build logistic regression
models. Mice were classified as colonized or cleared (not detectable at
the limit of detection of 100 CFU) based on CFU g/stool data from 7 days
post-infection. B-D. Classification input data used for models based on
day -1 (B), day 0 (C), and day 1 (D) community relative abundance data.
Only mice with day 7 \emph{C. difficile} status and community relative
abundance data for each respective timepoint were used as input data for
the classification models.

@@

\textbf{Movie S1. Large shifts in bacterial community structure occurred
after clindamycin and \emph{C. difficile} infection.} PCoA of Theta YC
distances animated from 0 through 9 days post-infection. PERMANOVA
analysis indicated colony source was the variable that explained the
most observed variation across fecal communities (source
R\textsuperscript{2} = 0.35, \emph{P} = 0.0001) followed by interactions
between cage and day of the experiment. Transparency of the circle
corresponds to the day of the experiment, each circle represents a
sample from an individual mouse at a specific timepoint. See Table S5
for PERMANOVA results).
